\begin{rSection}{Publications}

\textbf{Journal Articles}
\begin{description}[font=\normalfont]
\item[{[J10]}]{
    Donghao Fang, Boyang Zhang, Hailiang Hu, \textbf{Wuxi Li}, Bo Yuan, Jiang Hu,
    ``\href{https://dl.acm.org/doi/full/10.1145/3705729}{Global Placement Exploiting Soft 2D Regularity}'',
    ACM Transactions on Design Automation of Electronic Systems (TODAES), 2025.
}

\item[{[J9]}]{
    Licheng Guo, Pongstorn Maidee, Yun Zhou, Chris Lavin, Eddie Hung, \textbf{Wuxi Li}, Jason Lau, Weikang Qiao, Yuze Chi, Linghao Song, Yuanlong Xiao, Alireza Kaviani, Zhiru Zhang, Jason Cong,
    ``\href{https://dl.acm.org/doi/abs/10.1145/3593025}{RapidStream 2.0: Automated Parallel Implementation of Latency Insensitive FPGA Designs Through Partial Reconfiguration}'',
    ACM Transactions on Reconfigurable Technology and Systems (TRETS), 2023.
}

\item[{[J8]}]{
    Yibai Meng, \textbf{Wuxi Li}, Yibo Lin, David Z. Pan,
    ``\href{https://ieeexplore.ieee.org/abstract/document/9330804}{elfPlace: Electrostatics-based Placement for Large-Scale Heterogeneous FPGAs}'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), 2021.
}

\item[{[J7]}]{
    Yibo Lin, Zixuan Jiang, Jiaqi Gu, \textbf{Wuxi Li}, Shounak Dhar, Haoxing Ren, Brucek Khailany, David Z. Pan,
    ``\href{https://ieeexplore.ieee.org/abstract/document/9122053}{DREAMPlace: Deep Learning Toolkit-Enabled GPU Acceleration for Modern VLSI Placement}'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), 2020.
    (\textbf{Best Paper Award})
}

\item[{[J6]}]{
    Yibo Lin, \textbf{Wuxi Li}, Jiaqi Gu, Haoxing Ren, Brucek Khailany, David Z. Pan,
    ``\href{https://ieeexplore.ieee.org/document/8982049}{ABCDPlace: Accelerated Batch-based Concurrent Detailed Placement on Multi-threaded CPUs and GPUs}'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), 2020.
}

\item[{[J5]}]{
    \textbf{Wuxi Li}, David Z. Pan,
    ``\href{https://ieeexplore.ieee.org/document/8500228/}{A New Paradigm for FPGA Placement without Explicit Packing}'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), 2018.
}

\item[{[J4]}]{
    Meng Li, Bei Yu, Yibo Lin, Xiaoqing Xu, \textbf{Wuxi Li}, David Z. Pan,
    ``\href{https://ieeexplore.ieee.org/document/8419279/}{A Practical Split Manufacturing Framework for Trojan Prevention via Simultaneous Wire Lifting and Cell Insertion}'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), 2018.
}

\item[{[J3]}]{
    \textbf{Wuxi Li}, Yibo Lin, Meng Li, Shounak Dhar, David Z. Pan,
    ``\href{https://dl.acm.org/citation.cfm?id=3174849}{UTPlaceF 2.0: A High-Performance Clock-Aware FPGA Placement Engine}'',
    ACM Transactions on Design Automation of Electronic Systems (TODAES), 2018.
    (\textbf{1st-Place Award of ISPD 2017 Contest})
}

\item[{[J2]}]{
    \textbf{Wuxi Li}, Shounak Dhar, David Z. Pan,
    ``\href{http://ieeexplore.ieee.org/document/7984833/}{UTPlaceF: A Routability-Driven FPGA Placer with Physical and Congestion Aware Packing}'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), 2017.
}

\item[{[J1]}]{
    \textbf{Wuxi Li}, Hang Yuan, Wei Xu, Kunling Geng, Guoxing Wang,
    ``\href{http://ecst.ecsdl.org/content/52/1/1091.short}{An Optimization Procedure for Coil Design in a Dual Band Wireless Power and Data Transmission System}'',
    ECS Transactions (ECST), 2013.
}

\end{description}

\textbf{Conference Papers}
\begin{description}[font=\normalfont]
\item[{[C18]}]{
    Zizheng Guo, Zuodong Zhang, \textbf{Wuxi Li}, Tsung-Wei Huang, Xizhe Shi, Yufan Du, Yibo Lin, Runsheng Wang, Ru Huang,
    ``\href{https://dl.acm.org/doi/abs/10.1145/3676536.3676651}{HeteroExcept: A CPU-GPU Heterogeneous Algorithm to Accelerate Exception-aware Static Timing Analysis}'',
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), 2024.
}

\item[{[C17]}]{
    Donghao Fang, Hailaing Hu, \textbf{Wuxi Li}, Bo Yuan, Jiang Hu,
    ``\href{https://dl.acm.org/doi/abs/10.1145/3676536.3676690}{SysMix: Mixed-Size Placement for Systolic-Array-Based Hierarchical Designs}'',
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), 2024.
}

\item[{[C16]}]{
    \textbf{Wuxi Li}, Yuji Kukimoto, Gregory Servel, Ismail Bustany, Mehrdad E. Dehkordi,
    ``\href{https://dl.acm.org/doi/abs/10.1145/3626184.3633313}{Calibration-Based Differentiable Timing Optimization in Non-linear Global Placement}'',
    ACM International Symposium on Physical Design (ISPD), 2024.
}

\item[{[C15]}]{
    Hailiang Hu, Donghao Fang, \textbf{Wuxi Li}, Bo Yuan, Jiang Hu,
    ``Systolic Array Placement on FPGAs'',
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), 2023.
}

\item[{[C14]}]{
    Ismail Bustany, Grigor Gasparyan, Amit Gupta, Andrew B. Kahng, Meghraj Kalase, \textbf{Wuxi Li}, Bodhisatta Pramanik,
    ``\href{https://ieeexplore.ieee.org/abstract/document/10299868}{The 2023 MLCAD FPGA Macro Placement Benchmark Design Suite and Contest Results}'',
    ACM/IEEE Workshop on Machine Learning for CAD (MLCAD), 2023.
}

\item[{[C13]}]{
    Zizheng Guo, Zuodong Zhang, Xun Jiang, \textbf{Wuxi Li}, Yibo Lin, Runsheng Wang, Ru Huang,
    ``\href{https://ieeexplore.ieee.org/document/10247907}{General-Purpose Gate-Level Simulation with Partition-Agnostic Parallelism}'',
    ACM/IEEE Design Automation Conference (DAC), 2023.
}

\item[{[C12]}]{
    Donghao Fang, Boyang Zhang, Hailiang Hu, \textbf{Wuxi Li}, Bo Yuan, Jiang Hu,
    ``\href{https://dl.acm.org/doi/10.1145/3505170.3506723}{Global Placement Exploiting Soft 2D Regularity}'',
    ACM International Symposium on Physical Design (ISPD), 2022.
}

\item[{[C11]}]{
    Jiaqi Gu, Zheng Zhao, Chenghao Feng, \textbf{Wuxi Li}, Ray T. Chen, David Z. Pan,
    ``\href{https://ieeexplore.ieee.org/document/9218593}{FLOPS: Efficient On-Chip Learning for Optical Neural Networks Through Stochastic Zeroth-Order Optimization}'',
    ACM/IEEE Design Automation Conference (DAC), 2020.
}

\item[{[C10]}]{
    Mohamed B. Alawieh, \textbf{Wuxi Li}, Yibo Lin, Love Singhal, Mahesh Iyer, David Z. Pan,
    ``\href{https://ieeexplore.ieee.org/document/9045178}{High-Definition Routing Congestion Prediction for Large-Scale FPGAs}'',
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), 2020.
}

\item[{[C9]}]{
    Mingjie Liu, \textbf{Wuxi Li}, Keren Zhu, Biying Xu, Yibo Lin, Linxiao Shen, Xiyuan Tang, Nan Sun, David Z. Pan,
    ``\href{https://ieeexplore.ieee.org/document/9045109}{S3DET: Detecting System Symmetry Constraints for Analog Circuits with Graph Similarity}'',
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), 2020.
}

\item[{[C8]}]{
    \textbf{Wuxi Li}, Yibo Lin, David Z. Pan,
    ``\href{https://ieeexplore.ieee.org/document/8942075}{elfPlace: Electrostatics-based Placement for Large-Scale Heterogeneous FPGAs}'',
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), 2019.
    (\textbf{Best-in-Track Paper})
}

\item[{[C7]}]{
    Yibo Lin, Shounak Dhar, \textbf{Wuxi Li}, Haoxing Ren, Brucek Khailany, David Z. Pan,
    ``\href{https://dl.acm.org/citation.cfm?id=3317803}{DREAMPlace: Deep Learning Toolkit-Enabled GPU Acceleration for Modern VLSI Placement}'',
    ACM/IEEE Design Automation Conference (DAC), 2019.
    (\textbf{Best Paper Award})
}

\item[{[C6]}]{
    \textbf{Wuxi Li}, Stephen Yang, Mehrdad E. Dehkordi, David Z. Pan,
    ``\href{https://dl.acm.org/citation.cfm?id=3293897}{Simultaneous Placement and Clock Tree Construction for Modern FPGAs}'',
    ACM International Symposium on Field-Programmable Gate Arrays (FPGA), 2019.
}

\item[{[C5]}]{
    Meng Li, Bei Yu, Yibo Lin, Xiaoqing Xu, \textbf{Wuxi Li}, David Z. Pan,
    ``\href{https://ieeexplore.ieee.org/document/8297316}{A Practical Split Manufacturing Framework for Trojan Prevention via Simultaneous Wire Lifting and Cell Insertion}'',
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), 2018.
}

\item[{[C4]}]{
    \textbf{Wuxi Li}, Meng Li, Jiajun Wang, David Z. Pan,
    ``\href{https://ieeexplore.ieee.org/abstract/document/8203879/}{UTPlaceF 3.0: A Parallelization Framework for Modern FPGA Global Placement}'',
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), 2017.
    (\textbf{Invited Paper})
}

\item[{[C3]}]{
    Wei Ye, Yibo Lin, Xiaoqing Xu, \textbf{Wuxi Li}, Yiwei Fu, Yongsheng Sun, Canhui Zhan, David Z. Pan,
    ``\href{http://ieeexplore.ieee.org/document/8009178/}{Placement Mitigation Techniques for Power Grid Electromigration}'',
    IEEE International Symposium on Low Power Electronics and Design (ISLPED), 2017.
}

\item[{[C2]}]{
    \textbf{Wuxi Li}, Shounak Dhar, David Z. Pan,
    ``\href{http://ieeexplore.ieee.org/document/7827643/}{UTPlaceF: A Routability-Driven FPGA Placer with Physical and Congestion Aware Packing}'',
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), 2016.
    (\textbf{Invited Paper, 1st-Place Award of ISPD 2016 Contest})
}

\item[{[C1]}]{
    Wei Xu, Xiyan Li, \textbf{Wuxi Li}, Hang Yuan, Guoxing Wang,
    ``\href{http://ieeexplore.ieee.org/document/6865159/}{Live demonstration: An Optimization Software and a Design Case of a Novel Dual Band Wireless Power and Data Transmission System}'',
    IEEE International Symposium on Circuits and Systems (ISCAS), 2014.
}

\end{description}

\end{rSection}
